Dynamique des communautés

### 2025-04-21 Article_BIO500/Article_BIO500.Rmd
presentation rmd ok

author:
  - name: "Kyara Boisvert"
    affiliation: "Université de Sherbrooke, Département d'écologie, 2500 Boulevard de l'Université, Sherbrooke, Québec, J1N 3C6" 
  - name: "Zoé Chol"
    affiliation: "Université de Sherbrooke, Département d'écologie, 2500 Boulevard de l'Université, Sherbrooke, Québec, J1N 3C6"
  - name: "William Simard"
    affiliation: "Université de Sherbrooke, Département d'écologie, 2500 Boulevard de l'Université, Sherbrooke, Québec, J1N 3C6"

@@

keywords:
  - "abondance"
  - "taxonomie"
  - optional
  - optional
  - optional

@@

### Méthode:

@@

### Résultats:

@@

### Discussion:

### Conclusion

### Bibliographie:
This PNAS journal template is provided to help you write your work in the correct journal format. Instructions for use are provided below.

@@

```{=tex}
\showmatmethods
\showacknow
\pnasbreak
```

>>>>

author:
  - name: Kyara Boisvert
    affiliation: a
  - name: Zoé Chol
    affiliation: a
  - name: William Simard
    affiliation: a
address:
  - code: a
    address: Université de Sherbrooke, Département d'écologie, 2500 Boulevard de l'Université, Sherbrooke, Québec, J1N 3C6

@@

keywords:
  - abondance
  - taxonomie
  - optional
  - optional
  - optional

@@

# Méthode

@@

# Résultats

@@

# Discussion

# Conclusion

# Bibliographie
This PNAS journal template is provided to help you write your work in the correct journal format. Instructions for use are provided below.

@@

### 2025-04-21 Article_BIO500/Article_BIO500.tex
presentation rmd ok

\author[Université de Sherbrooke, Département d'écologie, 2500 Boulevard
de l'Université, Sherbrooke, Québec, J1N 3C6]{Kyara Boisvert}
\author[Université de Sherbrooke, Département d'écologie, 2500 Boulevard
de l'Université, Sherbrooke, Québec, J1N 3C6]{Zoé Chol}
\author[Université de Sherbrooke, Département d'écologie, 2500 Boulevard
de l'Université, Sherbrooke, Québec, J1N 3C6]{William Simard}

@@

\subsubsection{Méthode:}\label{muxe9thode}

@@

\subsubsection{Résultats:}\label{ruxe9sultats}

@@

\subsubsection{Discussion:}\label{discussion}

\subsubsection{Conclusion}\label{conclusion}

\subsubsection{Bibliographie:}\label{bibliographie}

@@

\showmatmethods
\showacknow
\pnasbreak

>>>>

\author[a]{Kyara Boisvert}
\author[a]{Zoé Chol}
\author[a]{William Simard}

  \affil[a]{Université de Sherbrooke, Département d'écologie, 2500
Boulevard de l'Université, Sherbrooke, Québec, J1N 3C6}

@@

\section{Méthode}\label{muxe9thode}

@@

\section{Résultats}\label{ruxe9sultats}

@@

\section{Discussion}\label{discussion}

\section{Conclusion}\label{conclusion}

\section{Bibliographie}\label{bibliographie}

@@
